Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-07-23 paper2_JNLS/Referee Reports/Ref1Response/Ref1.tex
NM

\section*{Referee 1}

@@

\noindent
\\We thank the referee for these kind remarks.

>>>>

\section*{Responses to Referee 1}

We thank the referee for the careful review of our work, which has helped us greatly to improve and clarify the manuscript. Below we respond to each of the referee's comments in sequence. For your convenience, we are submitting a version of the revised manuscript with the changes highlighted. \\ \\ \\

@@

\noindent
\\We thank the referee for these kind words and hope that we have adequately addressed all of the concerns raised. The referee's comments have certainly helped us improve the paper.
